Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-23 pecomplexity.tex
Added the FULL MASE error table!

\begin{table}[htdp]
\caption{Average nRMSE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                  & Horizon & nRMSE LMA           & nRMSE na\"{i}ve           &LMA MASE (ARIMA) & $l=5$                   & $l=6$                   \\
\hline
gcc               & 4,542   & $0.1407 \pm 0.0063$ & $0.1487 \pm 0.0066$ &1.5416(0.929)& $0.9510 \pm 0.0011$ & $0.9430 \pm 0.0013$ \\

col\_major        & 14,709  & $0.0252 \pm 0.0061$ & $0.1975 \pm 0.0436$ &0.0519(0.07UF)& $0.5636 \pm 0.0031$ & $0.5131 \pm 0.0034$ \\

%SVD\_Full         & 22,072  & $0.0323 \pm 0.0019$ & $0.1784 \pm 0.0040$ & $0.8765 \pm 0.0044$ & $0.8508 \pm 0.0035$ \\
SVD\_IPC\_Regime1 & 2,158   & $0.1680 \pm 0.0317$ & $0.3517 \pm 0.5223$ &0.7954(0.724UF)& $0.9761 \pm 0.0084$ & $0.9572 \pm 0.0156$ \\
SVD\_IPC\_Regime2 & 6,902   & $0.1716 \pm 0.0043$ & $0.1762 \pm 0.0012$ &1.9990(1.138)             & $0.8760 \pm 0.0052$ & $0.8464 \pm 0.0044$ \\
SVD\_IPC\_Regime3 & 947     & $0.0507 \pm 0.0011$ & $0.5413 \pm 0.0005$ &1.0089 (1.165215)              & $0.7768 \pm 0.0073$ & $0.7157 \pm 0.0056$ \\
SVD\_IPC\_Regime4 & 2,929   & $0.1288 \pm 0.0471$ & $0.2308 \pm 0.0867$ &0.8976 (0.840548)           & $0.9073 \pm 0.0080$ & $0.8246 \pm 0.0077$ \\
SVD\_IPC\_Regime5 & 3,255   & $0.0235 \pm 0.0022$ & $0.1306 \pm 0.0003$ &0.7487 (1.260)& $0.7333 \pm 0.0076$ & $0.6776 \pm 0.0068$ \\
SVD\_IPC\_Regime6 & 5,804   & $0.0196 \pm 0.0022$ & $0.0508 \pm 0.0003$ &0.7848 (0.7831) & $0.8101 \pm 0.0135$ & $0.7475 \pm 0.0106$ \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

>>>>

\begin{table}[htdp]
\caption{Average nRMSE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
                   & nRMSE LMA           & nRMSE na\"{i}ve   & $l=5$                   & $l=6$                   \\
\hline
gcc                  & $0.1407 \pm 0.0063$ & $0.1487 \pm 0.0066$ & $0.9510 \pm 0.0011$ & $0.9430 \pm 0.0013$ \\

col\_major          & $0.0252 \pm 0.0061$ & $0.1975 \pm 0.0436$ & $0.5636 \pm 0.0031$ & $0.5131 \pm 0.0034$ \\

SVD\_IPC\_Regime1    & $0.1680 \pm 0.0317$ & $0.3517 \pm 0.5223$ & $0.9761 \pm 0.0084$ & $0.9572 \pm 0.0156$ \\
SVD\_IPC\_Regime2    & $0.1716 \pm 0.0043$ & $0.1762 \pm 0.0012$ & $0.8760 \pm 0.0052$ & $0.8464 \pm 0.0044$ \\
SVD\_IPC\_Regime3      & $0.0507 \pm 0.0011$ & $0.5413 \pm 0.0005$ & $0.7768 \pm 0.0073$ & $0.7157 \pm 0.0056$ \\
SVD\_IPC\_Regime4    & $0.1288 \pm 0.0471$ & $0.2308 \pm 0.0867$ & $0.9073 \pm 0.0080$ & $0.8246 \pm 0.0077$ \\
SVD\_IPC\_Regime5    & $0.0235 \pm 0.0022$ & $0.1306 \pm 0.0003$& $0.7333 \pm 0.0076$ & $0.6776 \pm 0.0068$ \\
SVD\_IPC\_Regime6    & $0.0196 \pm 0.0022$ & $0.0508 \pm 0.0003$ & $0.8101 \pm 0.0135$ & $0.7475 \pm 0.0106$ \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

\begin{table}[htdp]
\caption{Average MASE for 1-step predictions at a 10\% prediction horizon over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                   & MASE LMA    & MASE ARIMA &MASE na\"{i}ve & $l=5$  & $l=6$ \\
\hline
gcc                  & $ 1.5296\pm 0.0214$ & $1.8366 \pm0.0157 $ & $1.7970\pm0.0095$& $0.9510 \pm 0.0011$ & $0.9430 \pm 0.0013$ \\

col\_major           & $ 0.0500 \pm0.0018  $ & $0.5989  \pm 0.2114 $ & $0.5707\pm0.0017$& $0.5636 \pm 0.0031$ & $0.5131 \pm 0.0034$ \\

SVD\_IPC\_Regime1     & $ 0.8273\pm 0.0755$ & $ 0.7141\pm 0.0745 $ & $2.6763\pm4.3282$& $0.9761 \pm 0.0084$ & $0.9572 \pm 0.0156$ \\
SVD\_IPC\_Regime2     & $1.2789 \pm0.0196 $ & $2.1626 \pm0.0265 $ &  $3.0543\pm0.0404$ &  $0.8760 \pm 0.0052$ & $0.8464 \pm0.0044$ \\
SVD\_IPC\_Regime3       & $0.6192 \pm0.0209 $ & $0.7129 \pm 0.0096 $ & $31.3857\pm 0.2820$ & $0.7768 \pm 0.0073$ & $0.7157 \pm 0.0056$ \\
SVD\_IPC\_Regime4     & $ 0.7789\pm0.0358 $ & $0.9787 \pm0.0321 $ & $2.6613\pm0.0739$                          &$0.9073 \pm 0.0080$ & $0.8246 \pm 0.0077$ \\
SVD\_IPC\_Regime5     & $ 0.7177\pm 0.0483 $ & $2.3700  \pm 0.0505 $ & $20.8703 \pm 0.1915$& $0.7333 \pm 0.0076$ & $0.6776 \pm 0.0068$ \\
SVD\_IPC\_Regime6     & $ 0.7393\pm 0.0682 $ & $ 1.4379\pm 0.0609$ & $2.1967\pm0.0830$& $0.8101 \pm 0.0135$ & $0.7475 \pm 0.0106$ \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

%
%
%\begin{table}[htdp]
%\caption{Average nRMSE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
%\begin{center}
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline
%                  & Horizon & nRMSE LMA           & nRMSE na\"{i}ve           &LMA MASE (ARIMA) & $l=5$                   & $l=6$                   \\
%\hline
%gcc               & 4,542   & $0.1407 \pm 0.0063$ & $0.1487 \pm 0.0066$ &1.5416(0.929)& $0.9510 \pm 0.0011$ & $0.9430 \pm 0.0013$ \\
%
%col\_major        & 14,709  & $0.0252 \pm 0.0061$ & $0.1975 \pm 0.0436$ &0.0519(0.07UF/0.5740/0.9936)& $0.5636 \pm 0.0031$ & $0.5131 \pm 0.0034$ \\
%
%%SVD\_Full         & 22,072  & $0.0323 \pm 0.0019$ & $0.1784 \pm 0.0040$ & $0.8765 \pm 0.0044$ & $0.8508 \pm 0.0035$ \\
%SVD\_IPC\_Regime1 & 2,158   & $0.1680 \pm 0.0317$ & $0.3517 \pm 0.5223$ &0.7954(0.724UF)& $0.9761 \pm 0.0084$ & $0.9572 \pm 0.0156$ \\
%SVD\_IPC\_Regime2 & 6,902   & $0.1716 \pm 0.0043$ & $0.1762 \pm 0.0012$ &1.9990(1.138)             & $0.8760 \pm 0.0052$ & $0.8464 \pm 0.0044$ \\
%SVD\_IPC\_Regime3 & 947     & $0.0507 \pm 0.0011$ & $0.5413 \pm 0.0005$ &1.0089 (1.165215)              & $0.7768 \pm 0.0073$ & $0.7157 \pm 0.0056$ \\
%SVD\_IPC\_Regime4 & 2,929   & $0.1288 \pm 0.0471$ & $0.2308 \pm 0.0867$ &0.8976 (0.840548)           & $0.9073 \pm 0.0080$ & $0.8246 \pm 0.0077$ \\
%SVD\_IPC\_Regime5 & 3,255   & $0.0235 \pm 0.0022$ & $0.1306 \pm 0.0003$ &0.7487 (1.260/2.3446)& $0.7333 \pm 0.0076$ & $0.6776 \pm 0.0068$ \\
%SVD\_IPC\_Regime6 & 5,804   & $0.0196 \pm 0.0022$ & $0.0508 \pm 0.0003$ &0.7848 (0.7831) & $0.8101 \pm 0.0135$ & $0.7475 \pm 0.0106$ \\
%\hline
%\end{tabular}
%\end{center}
%\label{default}
%\end{table}%

%
%
%\begin{table}[htdp]
%\caption{Average MASE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
%\begin{center}
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline
%                   & MASE LMA    & MASE ARIMA &MASE na\"{i}ve & $l=5$  & $l=6$ \\
%\hline
%gcc                  & $1.9856 \pm $ & $1.7525 \pm $ &1.7904 $\pm$& $0.9510 \pm 0.0011$ & $0.9430 \pm 0.0013$ \\
%
%col\_major           & $ 0.0587\pm $ & $0.9936 \pm $ & $0.5713\pm$& $0.5636 \pm 0.0031$ & $0.5131 \pm 0.0034$ \\
%
%
%
%
%SVD\_IPC\_Regime1     & $ \pm $ & $ \pm $ & $\pm$& $0.9761 \pm 0.0084$ & $0.9572 \pm 0.0156$ \\
%SVD\_IPC\_Regime2     & $ 2.3753\pm $ & $0.7268 \pm $ & $3.1064\pm$& $0.8760 \pm 0.0052$ & $0.8464 \pm 0.0044$ \\
%SVD\_IPC\_Regime3       & $ \pm $ & $ \pm $ & $\pm$& $0.7768 \pm 0.0073$ & $0.7157 \pm 0.0056$ \\
%SVD\_IPC\_Regime4     & $ \pm $ & $ \pm $ & $\pm$&$0.9073 \pm 0.0080$ & $0.8246 \pm 0.0077$ \\
%SVD\_IPC\_Regime5     & $4.9079 \pm $ & $2.3366 \pm $ & $21.0372\pm$& $0.7333 \pm 0.0076$ & $0.6776 \pm 0.0068$ \\
%SVD\_IPC\_Regime6     & $ \pm $ & $ \pm $ & $\pm$& $0.8101 \pm 0.0135$ & $0.7475 \pm 0.0106$ \\
%\hline
%\end{tabular}
%\end{center}
%\label{default}
%\end{table}%
%
